Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-01-15 Manuscript_Nater_etal.qmd
minor edits

---
title: "Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird"
format: html
author: Chloé R. Nater, James A. Martin, Erlend B. Nilsen
editor: visual
bibliography: rypeIDSM_MS2.bib
---

@@

<!--# They obviously use a lesser breed of bird dog up that way.Probably use more german shorthairs or vislas. :-)  -->
<!-- Funnily enough, I have been suggesting to Erlend that we should have a master student to analyze the effect of dog breed on detection probability :-P -->

>>>>

---
title: "Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird"
format: docx
author: Chloé R. Nater, James A. Martin, Erlend B. Nilsen
editor: visual
bibliography: rypeIDSM_MS2.bib
---

@@

<!--# They obviously use a lesser breed of bird dog up that way.Probably use more german shorthairs or vislas. :-)  -->

<!-- Funnily enough, I have been suggesting to Erlend that we should have a master student to analyze the effect of dog breed on detection probability :-P -->
